Retrofitting Effect Handlers onto OCaml

### 2021-03-26 retro-concurrency.tex
tweak fig 1 layout to make (a) (b) divide more obvious
Minor edits

\begin{figure*}
\begin{minipage}{0.30\linewidth}
  \begin{minipage}{\linewidth}
    \begin{lstlisting}[numbers=left]
external ocaml_to_c
  : unit -> int = "ocaml_to_c"
exception E1
exception E2
let c_to_ocaml () = raise E1
let _ = Callback.register
    "c_to_ocaml" c_to_ocaml
let omain () =
  try (* h1 *)
    try (* h2 *) ocaml_to_c ()
    | with E2 -> 0
  | with E1 -> 42;;
let _ = assert (omain () = 42)
    \end{lstlisting}
    \vspace{-2mm}
    \subcaption{\texttt{meander.ml}}
    \label{code:meander_ml}
  \end{minipage}
  \begin{minipage}{\linewidth}
    \begin{lstlisting}[language=c,numbers=left]
#include <caml/mlvalues.h>
#include <caml/callback.h>

@@

The interaction of non-local control flow and resources has been studied
extensively. Scheme uses |dynamic-wind|~\cite{R5RS}, which is a generalisation
of Common Lisp |unwind-protect|~\cite{Steele90}, which ensures de-allocation
(and re-allocation) of resources every time the non-local control leaves and
enters back into a context. |dynamic-wind| is not quite sufficient for resource
clean up~\cite{Kiselyov,Sitaram03} as returning exits must be distinguished
from non-returning ones, and resource cleanup is only necessary during
non-returning exits.

@@

We thank Sam Lindley, Franc\'{o}is Pottier, the PLDI reviewers and our shepherd, Matthew Flatt, whose comments substantially improved the presentation. This research was funded via Royal Commission for the Exhibition of 1851 and Darwin College Research Fellowships,
and by grants from Jane Street and the Tezos Foundation.

>>>>

\begin{figure*}
\begin{minipage}{0.30\linewidth}
  \begin{minipage}{\linewidth}
    \begin{lstlisting}[numbers=left]
external ocaml_to_c
  : unit -> int = "ocaml_to_c"
exception E1
exception E2
let c_to_ocaml () = raise E1
let _ = Callback.register
    "c_to_ocaml" c_to_ocaml
let omain () =
  try (* h1 *)
    try (* h2 *) ocaml_to_c ()
    | with E2 -> 0
  | with E1 -> 42;;
let _ = assert (omain () = 42)
    \end{lstlisting}
    \vspace{-2mm}
    \subcaption{\texttt{meander.ml}}
    \label{code:meander_ml}
  \end{minipage}
  \begin{minipage}{\linewidth}
    \begin{lstlisting}[language=c,numbers=left]

#include <caml/mlvalues.h>
#include <caml/callback.h>

@@

The interaction of non-local control flow and resources has been studied
extensively. Scheme uses |dynamic-wind|~\cite{R5RS}, which is a generalisation
of Common Lisp |unwind-protect|~\cite{Steele90}, which ensures de-allocation
and re-allocation of resources every time the non-local control leaves and
enters back into a context. |dynamic-wind| is not quite the right abstraction
as resources need to be cleaned up only on non-returning
exists~\cite{Kiselyov,Sitaram03}. This requires distinguishing returning exits
from non-returning ones.

@@

We thank Sam Lindley, Franc\'{o}is Pottier, the PLDI reviewers and our
shepherd, Matthew Flatt, whose comments substantially helped improve the
presentation. This research was funded via Royal Commission for the Exhibition
of 1851 and Darwin College Research Fellowships, and by grants from Jane Street
and the Tezos Foundation.
